Solent region: Test Maps

### 2021-08-09 Solent_Mapping_v2.Rmd
Adding in difference maps where there where gaps and attempting to fix some of the errors (unsucessfully)

```{r Mapping the difference in fuel poverty from 2012 to 2018}
##BROKEN
#merged_dfla$lad18nm <- merged_dfla$`LA Code` # Creating a variable with the local authority code in the same name 
#la_Fuelpov20182012dif <- merge(la_sf_data, merged_dfla) # Merge the local Authority boundaries and the Fuel Poverty data
#ggplot2::ggplot(la_Fuelpov20182012dif) +
 # geom_sf(aes(fill = pc_diff)) +
  #scale_fill_gradient(name = " Difference in proportion of households fuel poor (%)", low="green", high="red") +
#labs(caption="Solent (all LA)")
```

@@

```{r Mapping the electrcity consumption of the MSOAs}
msoa_elecData$MSOA11CD <- msoa_elecData$ 'Middle Layer Super Output Area (MSOA) Code' #Creating a variable with the LA code and the name as in the sf_data
msoa_merged_sf <-merge(msoa_sf_data, msoa_elecData)
ggplot2::ggplot(msoa_merged_sf) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
####Mapping the change from 2010 to 2019

@@

```{r Mapping the electrcity consumption of the MSOAs Industrial Sector}
msoa_elecDatanondom$MSOA11CD <- msoa_elecDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_sf_nondom <-merge(msoa_sf_data, msoa_elecDatanondom)
ggplot2::ggplot(msoa_merged_sf_nondom) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
####Difference from 2010 to 2019

@@

####Mapping the difference in non domestic gas from 2010 to 2019

here here here

>>>>

```{r Mapping the difference in fuel poverty from 2012 to 2018}
#merged_dfla$lad18nm <- merged_dfla$`LA Code` # Creating a variable with the local authority code in the same name 
#la_Fuelpov20182012dif <- merge(la_sf_data, merged_dfla) # Merge the local Authority boundaries and the Fuel Poverty data
#ggplot2::ggplot(la_Fuelpov20182012dif) +
 # geom_sf(aes(fill = pc_diff)) +
  #scale_fill_gradient(name = " Difference in proportion of households fuel poor (%)", low="green", high="red") +
#labs(caption="Solent (all LA)")
```

@@

```{r Mapping the electrcity consumption of the MSOAs}
msoa_elecData$MSOA11CD <- msoa_elecData$ 'Middle Layer Super Output Area (MSOA) Code' #Creating a variable with the LA code and the name as in the sf_data
msoa_merged_sf <-merge(msoa_sf_data, msoa_elecData)
ggplot2::ggplot(msoa_merged_sf) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
####Mapping the change from 2010 to 2019
```{r Creating the difference in MSOA mean dom elec consumption variable}
domelec_MSOA_2010<-readr::read_csv(paste0(dataFolder,"/energy/MSOA_DOM_ELEC_2010.csv"))
domelec_MSOA_2019<-readr::read_csv(paste0(dataFolder, "/energy/MSOA_DOM_ELEC_2019.csv"))
domelec_MSOA_2010$domelec2010<-domelec_MSOA_2010$'Mean consumption (kWh per meter)'
domelec_MSOA_2019$domelec2019<-domelec_MSOA_2019$'Mean consumption (kWh per meter)'
merged_domelec<-merge(domelec_MSOA_2010, domelec_MSOA_2019, by="Middle Layer Super Output Area (MSOA) Code", all=TRUE) ##BROKEN
names(merged_domelec)
merged_domelec$domelec_diff<-merged_domelec$domelec2019 - merged_domelec$domelec2010
summary(merged_domelec)
```
```{r Mapping the MSOA difference in mean dom elec consumption}
merged_domelec$MSOA11CD<-merged_domelec$"Middle Layer Super Output Area (MSOA) Code"
msoa_domelec20102019<-merge(msoa_sf_data, merged_domelec)
ggplot2::ggplot(msoa_domelec20102019)+geom_sf(aes(fill=domelec_diff))+scale_fill_continuous(name="Change in Mean comsumpton of domestic electricty per meter (kWh per meter",low="green",high="red")+labs(caption="Solent(all MSOAs)")
```

@@

```{r Mapping the electrcity consumption of the MSOAs Industrial Sector}
msoa_elecDatanondom$MSOA11CD <- msoa_elecDatanondom$ 'Middle Layer Super Output Area (MSOA) Code' 
msoa_merged_sf_nondom <-merge(msoa_sf_data, msoa_elecDatanondom)
ggplot2::ggplot(msoa_merged_sf_nondom) + 
  geom_sf(aes(fill = `Mean consumption (kWh per meter)`)) +
  scale_fill_continuous(name = "Electricity: Mean kWh per meter", low = "green", high = "red") +
  labs(caption = "Solent (all MSOAs)")
#mapping it
```
####Difference from 2010 to 2019
```{r Creating the mean electricty consumption from the industrial sector MOSA}
##BROKEN
NONDOMELEC_MSOA_2010<-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2010.csv")
NONDOMELEC_MSOA_2019<-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NONDOM_2019.csv")  
NONDOMELEC_MSOA_2010$nondomelec2010 <-NONDOMELEC_MSOA_2010$' Mean consumption (kWh per meter)'                                       
NONDOMELEC_MSOA_2019$nondomeelec2019<-NONDOMELEC_MSOA_2019$' Mean consumption (kWh per meter) '
merged_nondomelec <-merge(NONDOMELEC_MSOA_2010, NONDOMELEC_MSOA_2019, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
names(merged_nondomelec)
merged_nondomelec$nondomelec_diff<-merged_nondomelec$nondomeelec2019 - merged_nondomelec$nondomeelec2010
summary(merged_nondomelec)
```
```{r Mapping the difference in mean electricty consumption from the industrial sector MOSA}
merged_nondomelec$MSOA11CD <- merged_nondomelec$"Middle Layer Super Output Area (MSOA) Code"
msoa_nondom20102019 <- merge(msoa_sf_data, merged_nondomelec) #merging these
ggplot2::ggplot(msoa_nondom20102019) +
  geom_sf(aes(fill=nondom_diff))+ 
  scale_fill_continuous(name="Change in  mean electricty consumption for the industrial sector", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
```

@@

####Mapping the difference in non domestic gas from 2010 to 2019 
```{r Creating the difference in non domestic gas consumption in the MSOA}
nondomgas_msoa_2010 <-readr::read_csv(paste0(dataFolder,"/energy/MSOA_NonDom_Gas_2010.csv"))
nondomgas_msoa_2019<-readr::read_csv(paste0(dataFolder,"energy/MSOA_NonDom_Gas_2019.csv"))
nondomgas_msoa_2010$nondomgas2010<-nondomgas_msoa_2010$' Mean consumption (kWh per meter)'
nondomgas_msoa_2019$nondomgas2019<-nondomgas_msoa_2019$' Mean consumption (kWh per meter)'
merged_nondomgas20102019<-merge(nondomgas_msoa_2010, nondomgas_msoa_2019, by = "Middle Layer Super Output Area (MSOA) Code", all=TRUE)
names(merged_nondomgas20102019)
merged_nondomgas20102019$nondomgas_diff<-merged_nondomgas20102019$nondomgas2019 - merged_nondomgas20102019$nondomgas2010 ##BROKEN
summary(merged_nondomgas20102019)
```

```{r Mapping the change in non domestic gas usage in the MSOA}
merged_nondomgas20102019$MSOA11CD <- merged_df$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
msoa_nondomgas20102019 <- merge(msoa_sf_data, merged_nondomgas20102019) #merging these
ggplot2::ggplot(msoa_nondomgas20102019) +
  geom_sf(aes(fill=pc_diff))+ 
  scale_fill_continuous(name="Change in mean gas consumption in the indistrial sector", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
```
